\chapter*{\uppercase{ABSTRACT}}
\addcontentsline{toc}{section}{\bfseries \uppercase{Abstract}}
India is one of the highest milk producing countries. With the increase in population, consumers are growing day by day. Due to the varying milk requirements of the people, it becomes difficult for the milkmen to keep track of everyone’s varying needs. Also, with the growth in milk production, there is a lack of an efficient mechanism to collect milk from the producers, i.e., farmers. How can this be made more efficient using technology?

Our project aims to make the milk collection and distribution better by building an
application for the large-scale cooperative societies like Aavin that collect milk from
farmers, package them and sell them to consumers. Through our application, the
consumers will be able to make changes to their daily milk requirements. Also the milk
producers, i.e., farmers, will be able to benefit by selling their milk in a quick and efficient
manner.

This  application will provide interface to its customers, where they will be able to update their requirements on a regular basis. In addition to this, they will also be able to track their consumption. The farmers who produce milk can sell it to the society as and when theywant, by listing in the app which will be collected by one of the distributors. The distributors perform the processes of both collection and distribution a The administrators will be able to monitor other users and the application will have provisions to track location of the distributors on a lively basis. 